Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-09-16 ms.Rnw
Changed n parameters fit model 3

# model 3 AIC
mod3_n_params <- 39
mod3_aic <- 2 * mod3_n_params - 2 * mod3_ll

@@

mod3_spatPomp_n_params <- 39
mod3_spatPomp_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$ll
mod3_spatPomp_res$subset_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$subset_ll

>>>>

# model 3 AIC
mod3_n_params <- 29
mod3_aic <- 2 * mod3_n_params - 2 * mod3_ll

@@

mod3_spatPomp_n_params <- 29
mod3_spatPomp_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$ll
mod3_spatPomp_res$subset_aic <- 2 * mod3_spatPomp_n_params - 2 * mod3_spatPomp_res$subset_ll
